---
title: "R Notebook"
output: html_notebook
---

2.	Body measurement

Adapt some code from the Physio_dash.R shiny app to create a function and code that allows you to create some breathing rate simulated data. Then adapt some more code again  from the Physio_dash.R shiny app, using the dygraphs and xts packages, to create a script that plots a dygraph plot and print the dygraph plot of the simulated data.

Write the simulated data to a datafile so that it can be used to check the graph.

Submit an R script with the code you used, a pdf of the plot and the datafile of your simulated data.

---
title: "R Notebook"
output: html_notebook
---

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(dygraphs)
library(xts)
```

Code from Physio_dash.R

```{r}
#   data_BR_sim <- eventReactive(input$simulate_data,{
#     time <- seq(t_start, t_start+(input$duration*60000), by = 1500)
#     Breathing.Rate <- as.numeric(arima.sim(model = list(ar = input$autocorrelation) , n = length(time), mean = 4, sd = 5))
#     data.frame(time,Breathing.Rate)
#   })
```

Adapted code

```{r}
simulated_data <- function(
  t_start,
  duration,
  autocorrelation
) {
  time <- seq(t_start, t_start+(duration*60000), by = 1500)
  data <- as.numeric(arima.sim(model = list(ar = autocorrelation), n = length(time), mean = 4, sd = 5))
  data <- abs(data)
  data <- data.frame(time, data)
  return(data)
}
```

Generate some data

```{r}
df <- simulated_data(0, 1, 0.2)
write.csv(df, "Q2.Data.csv")
df
```

More code from Physio_dash.R

```{r}
#   output$plot_BR <- renderDygraph({
#     BR_xts <- xts(x = data_BR()$value, order.by = data_BR()$time_date) # specific dataframe with time series class
#     dygraph(BR_xts, main = " ", ylab = "Breathing Rate (rpm)", xlab = "time", group = "biometrics")%>%
#       dySeries("V1", label = "Breathing Rate (rpm)") %>%
#       dyRangeSelector(height = 20) %>%
#       dyOptions(colors = 'blue') %>%
#       dyUnzoom() %>%
#       dyLegend(width = 300)
#   })
```

Adapted code to display graph

```{r}
graph <- dygraph(df, main = " ", ylab = "Breathing Rate (rpm)", xlab = "time", group = "biometrics") %>%
dySeries("data", label = "Breathing Rate (rpm)") %>%
dyRangeSelector(height = 20) %>%
dyOptions(colors = 'blue') %>%
dyUnzoom() %>%
dyLegend(width = 300)
graph
```

Negative breathing rates are not valid but were produced by the code!!
The code is adapted to fix this.

