3.	Statistical modelling

Using the mgcv package take the simulated breathing rate data and create a linear model and a GAM model using the lm() command and the gam() command respectively (the gam command is part of the mgcv package). Report the summary output of the lm and gam models

Submit an R script with the code you used and with the reported statistics in the comments at the end of the script.


Loading Libraries
```{r}
library(mgcv)
library(tidyverse)
library(dplyr)
library(gratia)

```

```{r}
sim_Br_data<- read.csv("/Users/martinchristy/Desktop/Q2data.csv")
sim_Br_data<-sim_Br_data %>%
  select(-c(X,X.1))
sim_Br_data
```
#Lm model
```{r}
model2 <- lm(y ~ x, data = curveData)
curveData$predicted <- predict(model2)   # Save the predicted values
curveData$residuals <- residuals(model2) # Save the residual values
```


#lm model
```{r}
lm_model <- lm(data ~ time, data = sim_Br_data)
summary(lm_model)

```


#lm model graph
```{r}

sim_Br_data$predicted <- predict(lm_model)   # Save the predicted values
sim_Br_data$residuals <- residuals(lm_model) # Save the residual values

ggplot(data=sim_Br_data, aes(x=time, y=data)) + 
  geom_point() + 
  geom_point(colour = "red") +
  geom_smooth(method = "lm", se = FALSE, size = 1) +
  #geom_path(aes(x=x, y=z), linetype = "dashed") 
  geom_point(aes(y = predicted), shape = 1) +
  geom_segment(aes(xend = time, yend = predicted), alpha = .5) +
  geom_text(aes(y = predicted+(residuals/2), label = paste0("", round(residuals, 1), "")), size=2.5)

  print(sum(sim_Br_data$residuals^2)) # the sum of squares of the residuals 
  summary(lm_model)
```
#Sum of squares is large so model is not well approximated by the lm model
#The residuals are a bit far apart from the regression line so better will be using gam

#gam model 
```{r}
gam_model <- gam(data ~ s(time), data = sim_Br_data, method = "REML")
summary(gam_model)
```

#Gam.check the result
```{r}
gam.check(gam_model)
```

Plotting the GAM

```{r}
plot(gam_model, residuals = TRUE, se=TRUE, rug=FALSE, pch = 1, cex = 0.5,shade = TRUE, shade.col = "rosybrown2")
```


#gam model graph
```{r}
sim_Br_data$predicted <- predict(gam_model)   # Save the predicted values
sim_Br_data$residuals <- residuals(gam_model) # Save the residual values

ggplot(data=sim_Br_data, aes(x=time, y=data)) + 
  geom_point() + 
  geom_point(colour = "red") +
  #geom_smooth(method = "lm", se = FALSE, size = 1) +
  geom_path(aes(x=time, y=predicted), colour = "blue") +
  geom_point(aes(y = predicted), shape = 1) +
  geom_segment(aes(xend = time, yend = predicted), alpha = .5) +
  geom_text(aes(y = predicted+(residuals/2), label = paste0("", round(residuals, 1), "")), size=2.5)

  
  print(sum(sim_Br_data$residuals^2)) # the sum of squares of the GAM residuals
```

#The sum of squares error was reduced from lm_model(473.2408) to 453.681 when gam was used. SInce the p value is small, it indicates the k(number of basis function) is too low and ie, edf is close to k.
#The edf value is 1.619 which is close to 1. If edf=1 or close to 1, it indicates linear model. Also from the sum of squares error we can observe there is only a slight change when gam was used.

#Comparing lm() and gam()
```{r}
sim_Br_data$predicted <- predict(gam_model)   # Save the predicted values
sim_Br_data$residuals <- residuals(gam_model) # Save the residual values

ggplot(data=sim_Br_data, aes(x=time, y=data)) + 
  geom_point() + 
  geom_point(colour = "red") +
  geom_smooth(method = "lm", se = FALSE, size = 1) +
  geom_path(aes(x=time, y=predicted), colour = "blue") +
  geom_point(aes(y = predicted), shape = 1) +
  geom_segment(aes(xend = time, yend = predicted), alpha = .5) +
  geom_text(aes(y = predicted+(residuals/2), label = paste0("", round(residuals, 1), "")), size=2.5)

  print(sum(sim_Br_data$residuals^2)) # the sum of squares of the GAM residuals
```