---
title: "R Notebook"
output: html_notebook
---

4.	Sentiment Analysis

The TweetCorpusPolarity.csv file contains nearly 6000 tweets. About half of these tweets have been given a polarity rating of positive and the other half negative. Using the Warriner ratings in the Ratings_WarrinerVAD.csv file and the TweetCorpusPolarity.csv file based on the in class exercise produce a ggplot of each of the valence, arousal and dominance dimensions from the WarrinerVAD file. How do these relate to the polarity? Submit the code you created to achieve this as well as a image file of the plot. 

Importing required libraries
```{r}
require(dplyr)
require(tibble)
require(ggplot2)
library(tidytext)
library(plotly)
```

```{r}
library(tidyverse)
```

Load the tweets

```{r}
tweets <- read.csv("/Users/martinchristy/Desktop/Behavior Analytics/senti prac/TweetCorpusPolarity.csv")
tweets
```
Load the Ratings

```{r}
ratings <- read.csv("/Users/martinchristy/Desktop/Behavior Analytics/senti prac/Ratings_WarrinerVAD.csv")
ratings
```

Split the tweets into words


```{r}
df <- unnest_tokens(tweets, "word", "Tweet")
df
```

Inner join with ratings

```{r}
joined <- inner_join(df, ratings, by = "word")
joined
```

Plot type requested is ambiguous - assuming faceted average for each dimension?

```{r}
reduced_df <- joined %>%
group_by(Polarity) %>%
summarise(
  valence = mean(Valence),
  arousal = mean(Arousal),
  dominance = mean(Dominance)
)
reduced_df
```
```{r}
tidy_df <- reduced_df %>% gather("Dimension", "Mean", 2:4)
tidy_df
```

```{r}
ggplot(data = tidy_df, aes(x = Dimension, y = Mean)) +
geom_col(aes(fill = Dimension)) +
facet_wrap(~ Polarity)
```

